Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2018-03-23 draft3.1.tex
draft3.1

The obtained wave functions in the SPA and the CQ can be decomposed in the
$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
in Fig.~\ref{fig:N50_occ}.
For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
Here, $m$ and $j$ are related to each other, $2j=J-2m$.
They show excellent agreement with the exact results, not only for the
ground state but for excited states.
We find the SPA is even more precise than the CQ.
\begin{figure}[t]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
(a)\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
(b)\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
\hspace{13pt}
\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
\hspace{13pt}\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=50$ systems
with (a) $N=50$ and (b) $N=100$.
The upper and lower panels display the results for $x=0.5$ and $x=2$,
respectively. 
The three vertical bars at each $j$ from the left to the right represent
the squared components of the wave functions
from exact, SPA, and CQ calculations, respectively.
The left end of the horizontal axis at $j=j_{\rm min}$
corresponds to a component with $(n_1,n_2)=(N,0)$.
The next at $j=j_{\rm min}+1$ corresponds to the one with
$(n_1,n_2)=(N-2,2)$, and so on.
%From Eq. (\ref{momentum}),
%$j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.
}
 \label{fig:N50_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
 (a)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
 (b)  \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
%Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=N=8$ systems.
The panels (a) and (b) display the results for $x=0.5$ and $x=2$,
respectively. 
See also the caption of Fig.~\ref{fig:N50_occ}.
%The left end at $j=j_{\rm min}$ corresponds to a component with
%$(n_1,n_2)=(N,0)$.
%The next at $j=j_{\rm min}+1$ corresponds to the one with
%$(n_1,n_2)=(N-2,2)$, and so on.
}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[thb]
 \begin{minipage}{1\hsize}
 \begin{center}
(a) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
(b) \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
	\caption{The same as Fig.~\ref{fig:N8_occ} but for
	$N=2\Omega=16$.
}
 \label{fig:N16_occ}
\end{figure}

@@

%Between pairing rotational transition and pairing vibrational transition, we can find the transition strength are compareable in $x<1$, and pairing rotational transition are dominant in $x>1$. The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.  In canonical quantization, even though the tendency of $\ket{0_1^+}\to\ket{0_1^+}$ are reproduced, all transition strengths are failed to reproduce quantitatively. In semiclassical approach, the strengths have disagreement around phase transition region, but are recovering toward no pairing and strong pairing limit. \par
%In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.

\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{N16Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{N16Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
  \includegraphics[width=70mm,angle=-90]{N16Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
	with $\Omega=8$.
}
 \label{fig:N16Pad}
\end{figure}
%In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition. The most difficult case is closed shell system with BCS phase transition. However, semiclassical approach works well in closed shell system except phase transition region.

>>>>

The obtained wave functions in the SPA and the CQ can be decomposed in the
$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
in Fig.~\ref{fig:N50_occ}.
For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
Here, $m$ and $j$ are related to each other, $2j=J-2m$.
They show excellent agreement with the exact results, not only for the
ground state but for excited states.
We find the SPA is even more precise than the CQ.
\begin{figure}[t]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
  \includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq0p5occ_wo_adiabatic.eps}
  \includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}

\includegraphics[height=0.45\textwidth,angle=-90]{N50Xeq2occ_wo_adiabatic.eps}
\includegraphics[height=0.45\textwidth,angle=-90]{N100Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=50$ systems
with (a) $N=50$ and (b) $N=100$.
The upper and lower panels display the results for $x=0.5$ and $x=2$,
respectively. 
The three vertical bars at each $j$ from the left to the right represent
the squared components of the wave functions
from exact, SPA, and CQ calculations, respectively.
The left end of the horizontal axis at $j=j_{\rm min}$
corresponds to a component with $(n_1,n_2)=(N,0)$.
The next at $j=j_{\rm min}+1$ corresponds to the one with
$(n_1,n_2)=(N-2,2)$, and so on.
%From Eq. (\ref{momentum}),
%$j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.
}
 \label{fig:N50_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq0p5occ_wo_adiabatic.eps}
   \includegraphics[height=0.46\textwidth,angle=-90]{N8Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
%Occupation probability in excited $0^+$ states as a function of $j$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From (\ref{momentum}), $j=-2$ corresponds to 0p8h configuration, $j=-1$ corresponds to 2p10h configuration, and so on.
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=N=8$ systems.
The panels (a) and (b) display the results for $x=0.5$ and $x=2$,
respectively. 
See also the caption of Fig.~\ref{fig:N50_occ}.
%The left end at $j=j_{\rm min}$ corresponds to a component with
%$(n_1,n_2)=(N,0)$.
%The next at $j=j_{\rm min}+1$ corresponds to the one with
%$(n_1,n_2)=(N-2,2)$, and so on.
}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[thb]
 \begin{minipage}{1\hsize}
 \begin{center}
   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq0p5occ_wo_adiabatic.eps}
   \includegraphics[height=0.46\textwidth,angle=-90]{N16Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
	\caption{The same as Fig.~\ref{fig:N8_occ} but for
	$N=2\Omega=16$.
}
 \label{fig:N16_occ}
\end{figure}

@@

%Between pairing rotational transition and pairing vibrational transition, we can find the transition strength are compareable in $x<1$, and pairing rotational transition are dominant in $x>1$. The minuscule strength of $\ket{0_2^+}\to\ket{0_1^+}$ is caused from peculiarity of two-level system.  In canonical quantization, even though the tendency of $\ket{0_1^+}\to\ket{0_1^+}$ are reproduced, all transition strengths are failed to reproduce quantitatively. In semiclassical approach, the strengths have disagreement around phase transition region, but are recovering toward no pairing and strong pairing limit. \par
%In closed shell system, the phase transition is semiclassical approach is more quantitative than canonical approach except phase transition region.
\begin{figure}[htbp]
 \begin{minipage}{0.3\hsize}
 \begin{center}
 \includegraphics[width=70mm,angle=-90]{N16Pad_CQ.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
 \includegraphics[width=70mm,angle=-90]{N16Pad_FD.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.3\hsize}
 \begin{center}
 \includegraphics[width=70mm,angle=-90]{N16Pad_SPA.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
	\caption{The same as Fig.~\ref{fig:N50Pad} but for $N=14\rightarrow 16$
	with $\Omega=8$.
}
 \label{fig:N16Pad}
\end{figure}
%In realistic type, semiclassical approach is much better than canonical quantization in every physical values, especially in two-particle transition. The most difficult case is closed shell system with BCS phase transition. However, semiclassical approach works well in closed shell system except phase transition region.
